Deterministic Scheduling of Periodic Messages for Cloud RAN

### 2017-07-26 infocom/infocom.tex
bricoles à la fin

 \section{Conclusion}
In this paper, we proposed two deterministic methods to establish a low latency periodic communication between BBUs and RRHs in 
a star shaped fronthaul network. The first method uses no buffering and has no latency overhead. It works when the routes are short (Longest-Shortest policy) or when the load is less than $80\%$ (Exhaustive search of compact assignments).  
When the load is higher, buffering is allowed in the BBUs and we are able to find a determinstic communication scheme 
with no additionnal latency most of the time using our PMLS algorithm. 
We plan to study other commons fronthaul topologies such as caterpillars, trees or ring; the latter being different since 
the forward and backward routes are not symmetric. For other applications, it could be interesting to to optimize the average latency of the routes rather than the worst latency, a problem which could be solved using linear optimization.

>>>>

 \section{Conclusion}
In this paper, we proposed two deterministic methods to establish a low latency periodic communication between BBUs and RRHs in 
a star shaped fronthaul network. The first method uses no buffering and has no latency overhead. It works when the routes are short (Longest-Shortest policy) or when the load is less than $80\%$ (Exhaustive search of compact assignments).  
When the load is higher, buffering is allowed in the BBUs and we propose the algorithm PMLS which  finds a deterministic communication scheme with almost no additionnal latency.

We plan to study other commons fronthaul topologies such as caterpillars, trees or ring; the latter being different since 
the forward and backward routes are not symmetric. For other applications, it could be interesting to optimize the average latency of the routes rather than the worst latency, a problem which may be solved using linear optimization.
